### 2018-07-13 paper/message-passing-design.tex
Sphinxes: completes CreateHeader, fixes POR algorithm names

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateHeader\) and 
gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice extends the route using \(\WrapHeader\), attaches the 
message \(m\) as payload (\(\AttachPayload\)) and sends the package to the 
first node, \ie invokes the \(\SPOR[\Fwd]\) algorithm on the first node.
The node will then process the package and in turn forward the package to the 
next node, if itself is not the final destination.

>>>>

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateReply\) and 
gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice attaches a message \(m\) to the reply header (using 
\(\AttachPayload\), creates a forward header using \(\CreateFwd\) and attaches 
the reply header as payload (\(\AttachPayload\)) to the forward header.
Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 
algorithm on the first node.
The node will then process the header and in turn forward the packet to the 
next node.
When a node receives a packet where the nodes of the next layer is 
\(\{\rdvnode\}\), it will parse they payload as a packet to be forwarded.
When a node receives a packet where the nodes of the next layer is 
\(\{\nullnode\}\), then it knows that it is the intended recipient.

### 2018-07-13 paper/sphinxes.tex
Sphinxes: completes CreateHeader, fixes POR algorithm names

\NewScheme{\Sphinxes}{POR}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\WrapHeader}{\Sphinxes[WrapHeader]}
\NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
\NewAlgorithm{\Process}{\Sphinxes[Process]}

Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates an extendible header.
    It outputs a header with space left for a few layers and the needed keys to 
    add additional layers.

  \item \(\WrapHeader\) is used to wrap a given header using the proper keys.

@@

\NewVariable{\G}{\mathcal{G}}
\NewVariable*{\mac}{\mu}
\NewVariable*{\prg}{\rho}
\NewVariable*{\prp}{\pi}
\NewVariable{\hash}{h}
%\NewVariable{\tag}{\tau}
\NewVariable{\blind}{b}
\NewVariable{\N}{\mathcal{N}}
\NewVariable{\D}{\mathcal{D}}
\NewVariable*{\nullnode}{\varepsilon}
\NewVariable{\rdvnode}{*}

@@

This algorithm creates a header for \iac{POR}.
It takes as input a unique identifier \(I\in \bin^\kappa\) and a set of layers 
\(L = \{N_0, \dotsc, N_\nu\}\) such that \(\nu+1\leq r\).

\Cref{fig:CreateHeader} summarizes the algorithm.
\(w_L\) is the maximum width of a layer, \ie alternative nodes.
\(w_H\) is the header width:
layer nodes' ciphertexts and addresses ($2w_L\kappa$),
address of next node ($\kappa$),
\ac{MAC} ($\kappa$).

We reveal the maximum number of alternatives per layer.
But we do this in ordinary \ac{OR} too, since there is only one node per layer.

First we generate all the needed keys.

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\CreateHeader}{$I, L$}
      \State $w_L\gets \max_{N\in L} |N|$
      \Comment{Layer width}
      \State $w_H\gets (2w_L+2)$
      \Comment{Header width}
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
      \left\{\left\{N_\nu\concat
          I\concat
          0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
        \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
      \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 1$}
        \State $(\alpha, C, \beta, \gamma) \gets
          \WrapHeader[i, (\alpha, \beta, \gamma), \alpha_i, s_i, C_i, N_{i+1}, 
          w_L]$
      \EndFor
      \State \Return $(\alpha, C, \beta, \gamma)$
    \EndFunction

    \Function{\WrapHeader}{$i, (\alpha_{i+1}, \beta_{i+1}, \gamma_{i+1}), 
      \alpha_i, s_i, C_i, N_{i+1}, w_L$}
      \If{$i < 0$}
        \Return $\bot$
      \EndIf
      \State $\beta_i \gets \{N_{i+1}, \concat \gamma_{i+1}\concat 
      (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
      \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \State \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
      $I\in \bin^\kappa$ is an identifier.
      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $N_\nu$ is the destination.
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\ComputeKeys}{$L = \{L_0, \dotsc, L_l\}, w_L$}
      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
      \State $\alpha_0\gets \pk$
      \State $s_0\rgets \bin^\kappa$
      \For{$1\leq i\leq |N_0|$}
        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
      \EndFor
      \For{$|N_0|+1\leq i\leq w_L$}
        \State $c_0^{(i)}\rgets \bin^\kappa$
      \EndFor
      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
      \For{$1\leq i < \nu$}
        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
        \State $\alpha_i = \pk^{b_{i-1}}$
        \State $s_i\rgets \bin^\kappa$
        \For{$1\leq j\leq |N_i|$}
          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
        \EndFor
        \For{$|N_i|+1\leq i\leq w_L$}
          \State $c_0^{(i)}\rgets \bin^\kappa$
        \EndFor
        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
      \EndFor
      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
      C_\nu, b_\nu)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesKeys}%
    \dots
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\ComputePadding}{$\{s_0, \dotsc, s_\nu\}, w_H$}
      \State $\phi_0\gets \epsilon$
      \Comment{$\epsilon$ is the empty string.}
      \For{$1\leq i\leq \nu$}
        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i)+3)\kappa..(w_H 
            r+3)\kappa-1]} \}$
      \EndFor
      \State \Return $\phi_0, \dotsc, \phi_\nu$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesPadding}%
    \dots
  }
\end{figure}

>>>>

\NewScheme{\Sphinxes}{POR}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
\NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
\NewAlgorithm{\Process}{\Sphinxes[Process]}

Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates a header.

  \item \(\CreateReply\) constructs a header to be used for replies.

  \item \(\CreateFwd\) constructs a header to be used for forward messages.

@@

\NewVariable{\G}{\mathcal{G}}
\NewVariable*{\mac}{\mu}
\NewVariable*{\prg}{\rho}
\NewVariable*{\prp}{\pi}
\NewVariable{\hash}{h}
%\NewVariable{\tag}{\tau}
\NewVariable{\secret}{s}
\NewVariable{\blind}{b}
\NewVariable{\N}{\mathcal{N}}
\NewVariable{\D}{\mathcal{D}}
\NewVariable*{\nullnode}{\varepsilon}
\NewVariable{\rdvnode}{*}

@@

This algorithm creates a header for \iac{POR}.
It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.

The algorithm takes as input a unique identifier \(I\in \bin^\kappa\) and a set 
of layers \(L = \{L_0, \dotsc, L_\nu\}\) such that \(\nu+1\leq r\).
The last layer, \(L_\nu\), should be either \(\{\nullnode\}\) or 
\(\{\rdvnode\}\) to terminate the routing.

We let \(w_L = \max_{N\in L}|N|\) be the maximum width of a layer, \ie the 
number of alternative nodes in the layer with the most alternative nodes.
We let \(w_H = 2w_L+1\) be the header width:
each layer must accommodate the layer nodes' ciphertexts and addresses, \ie  
\(2w_L\) elements of \(\kappa\) bits,
and the \ac{MAC}, \ie one element of \(\kappa\) bits.
(Note that we reveal the maximum number of alternatives per layer, but this is 
no different from ordinary \ac{OR} where there is a constant one node per 
layer.)

First we generate all the needed keys.
We compute \(\nu+1\) tuples
\begin{align*}
  \alpha_0 &\gets g^\sk,
  & \secret_0 &\gets \bin^\kappa,
  & \blind_0 &\gets \hash_\blind(\alpha_0, \secret_0) \\
  \alpha_1 &\gets g^{\sk\blind_0},
  & \secret_1 &\gets \bin^\kappa,
  & \blind_1 &\gets \hash_\blind(\alpha_1, \secret_1) \\
  &\vdots &&\vdots && \vdots \\
  \alpha_\nu &\gets g^{\sk \blind_0\dotsb \blind_{\nu-1}},
  & \secret_\nu &\gets \bin^\kappa,
  & \blind_\nu &\gets \hash_\blind(\alpha_\nu, s_\nu).
\end{align*}
In addition, we compute
\begin{align*}
  \secret_0^{(0)} &\gets \pk_{n_0^{(0)}}^\sk,
  & \dotsc, &
  & \secret_0^{(|L_0|-1)} &\gets \pk_{n_0^{(|L_0|-1)}}^\sk \\
  \secret_1^{(0)} &\gets \pk_{n_1^{(0)}}^{\sk \blind_0},
  & \dotsc, &
  & \secret_1^{(|L_1|-1)} &\gets \pk_{n_1^{(|L_1|-1)}}^{\sk \blind_0} \\
  & \vdots &&& \vdots \\
  \secret_\nu^{(0)} &\gets \pk_{n_\nu^{(0)}}^{\sk \blind_0\dotsb 
    \blind_{\nu-1}},
  & \dotsc, &
  & \secret_\nu^{(|L_\nu|-1)} &\gets \pk_{n_\nu^{(|L_\nu|-1)}}^{\sk 
    \blind_0\dotsb \blind_{\nu-1}}.
\end{align*}
We note that a node \(n_i^{(j)}\) can compute \(s_i^{(j)}\) since \[
  s_i^{(j)} = \pk_{n_i^{(j)}}^{\sk \blind_0\dotsb \blind_{i-1}} = 
  \alpha_i^{\sk_{n_i^{(j)}}}.
\]
We then construct the ciphertexts
\begin{align*}
  C_0 &= \prp'\left(\hash_{\prp'}\left(s_0^{(0)}\right), s_0\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_0^{(|L_0|-1)}\right), s_0\right) \\
  C_1 &= \prp'\left(\hash_{\prp'}\left(s_1^{(0)}\right), s_1\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_1^{(|L_1|-1)}\right), s_1\right) \\
  & \vdots \\
  C_\nu &= \prp'\left(\hash_{\prp'}\left(s_\nu^{(0)}\right), s_\nu\right)
  \concat \dotsb
  \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
    s_\nu\right).
\end{align*}
and pad them to equal length with uniformly random bits, \ie length \(w_L = 
  \max_{i\in \{0, \dotsc, \nu\}} |C_i|\), where \(|C_i|\) denotes the length in 
bits (each ciphertext is \(\kappa\) bits).
These computations are summarized in \cref{fig:SphinxesKeys}.
\commentDaniel{We can probably comment out the figure.}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\ComputeKeys}{$L = \{L_0, \dotsc, L_l\}, w_L$}
      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
      \State $\alpha_0\gets \pk$
      \State $s_0\rgets \bin^\kappa$
      \For{$1\leq i\leq |N_0|$}
        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
      \EndFor
      \For{$|N_0|+1\leq i\leq w_L$}
        \State $c_0^{(i)}\rgets \bin^\kappa$
      \EndFor
      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
      \For{$1\leq i < \nu$}
        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
        \State $\alpha_i = \pk^{b_{i-1}}$
        \State $s_i\rgets \bin^\kappa$
        \For{$1\leq j\leq |N_i|$}
          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
        \EndFor
        \For{$|N_i|+1\leq i\leq w_L$}
          \State $c_0^{(i)}\rgets \bin^\kappa$
        \EndFor
        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
      \EndFor
      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
      C_\nu, b_\nu)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesKeys}%
    A function computing the keys for all nodes on all layers of a route.
    \(L = \{L_i\}_i\) is the set of layers and each \(L_i\) is a set of the 
    nodes on that layer.
    \(w_L = \max_{L_i\in L} |L_i|\) is the maximum layer width, \ie the number 
    of nodes in the layer with most nodes.
  }
\end{figure}

Next we need to compute the padding \(\phi_i\) for each layer \(i\).
We must do this is to predict the padding introduced at each layer so that we 
can compute the correct \acp{MAC} (\(\gamma_i\)).
The padding for the outmost layer (layer 0) is the empty string, thus \(\phi_0 
  \gets \epsilon\).
Then, for layers \(1\leq i\leq \nu\), we get
\begin{multline*}
  \phi_i\gets \left\{\phi_{i-1}\concat 0_{w_H\kappa}\right\}\oplus \\
  \left\{\prg\left(\hash_\prg\left(s_{i-1}\right)\right)_{[(w_H(r-i)+3)\kappa..(2r+3)\kappa-1]}\right\}.
\end{multline*}
These computations are summarized in \cref{fig:SphinxesPadding}.
\commentDaniel{We can probably remove the figure.}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\ComputePadding}{$\{s_0, \dotsc, s_\nu\}, w_H$}
      \State $\phi_0\gets \epsilon$
      \Comment{$\epsilon$ is the empty string.}
      \For{$1\leq i\leq \nu$}
        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i)+3)\kappa..(w_H 
            r+3)\kappa-1]} \}$
      \EndFor
      \State \Return $\phi_0, \dotsc, \phi_\nu$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesPadding}%
    A function computing the needed padding.
    \(\{s_i\}_i\) is the set of keys for the layers.
    \(w_H\) is the width of the header at each layer, \ie everything that must 
    be removed and compensated by padding.
  }
\end{figure}

Next we will use the above computations to compute the mix headers \(M_i = 
  (\alpha_i, \beta_i, \gamma_i)\).
\(\alpha_i\) was computed above, so we will compute \(\beta_i\) and 
\(\gamma_i\).
We must compute \(\beta_i\) in reverse order.
We let \(\beta_{\nu+1} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu\leq 
  i\leq 0\), we let
\begin{align*}
  \beta_i &\gets \left\{L_{i+1}\concat \gamma_{i+1}\concat 
    (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\
  \gamma_i &\gets \mac\left( \hash_\mac\left(s_i\right), \beta_i \right).
\end{align*}
The algorithm \(\CreateHeader\) is summarized in \cref{fig:CreateHeader}.
\commentDaniel{We can probably remove the figure.}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \footnotesize
  \begin{algorithmic}[1]
    \Function{\CreateHeader}{$I, L = \{L_i\}_i$}
      \State $w_L\gets \max_{L_i\in L} |L_i|$
      \Comment{Layer width}
      \State $w_H\gets (2w_L+1)$
      \Comment{Header width}
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
        \left\{\left\{L_\nu\concat
            I\concat
            0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
          \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
        \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 0$}
          \State $\beta_i \gets \{L_{i+1}, \concat \gamma_{i+1}\concat 
          (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
          \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \EndFor
      \State \Return $(\alpha, C, \beta, \gamma), \{s_0, \dotsc, s_\nu\}$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
      $I\in \bin^\kappa$ is an identifier.
      $L = \{L_0, \dotsc, L_\nu\}$ such that $L_i, L_j\subset \N$, $L_i\cap L_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $L_\nu$ is the destination.
  }
\end{figure}

\paragraph*{The \(\CreateReply\) algorithm}

\dots

\paragraph*{The \(\CreateFwd\) algorithm}

\dots

\paragraph*{The \(\AttachPayload\) algorithm}

\dots

\paragraph*{The \(\Process\) algorithm}

\dots
